A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-20 paper/paper.Rnw
Repeat sentence?

\paragraph{Annotated Training Data}

Class characteristics are characteristics which can be used to exclude shoes from a match at a crime scene, but cannot be used for individualized matching because they are shared by many shoes (e.g., all shoes of a specific brand and size). A sufficiently well-defined set of features can be used to separate shoes into make and model categories \citep{grossVariabilitySignificanceClass2013}; the set of features used in that study included circle/oval, crepe, herringbone, hexagon, parallel lines, logo/lettering/numbering, perimeter lugs, star, and other. After consulting with practitioners, we developed a set of categories suitable for automatic recognition by convolutional neural networks. These modifications were necessary because some of the definitions used in \citeauthor{grossVariabilitySignificanceClass2013} require contextual spatial information which is not preserved during labeling (for example, lugs are required to be on the perimeter of the shoe). \autoref{tab:class-char-examples} shows three examples of each class.

>>>>

\paragraph{Annotated Training Data}
\fix{The first sentence is a repeat from earlier in the paper, so we may want to move directly into the feature set we're using. Thoughts?}
Class characteristics are characteristics which can be used to exclude shoes from a match at a crime scene, but cannot be used for individualized matching because they are shared by many shoes (e.g., all shoes of a specific brand and size). A sufficiently well-defined set of features can be used to separate shoes into make and model categories \citep{grossVariabilitySignificanceClass2013}; the set of features used in that study included circle/oval, crepe, herringbone, hexagon, parallel lines, logo/lettering/numbering, perimeter lugs, star, and other. After consulting with practitioners, we developed a set of categories suitable for automatic recognition by convolutional neural networks. These modifications were necessary because some of the definitions used in Gross et al. (2013) require contextual spatial information which is not preserved during labeling (for example, lugs are required to be on the perimeter of the shoe). \autoref{tab:class-char-examples} shows three examples of each class.
